\chapter{Future Work}
While the algorithm developed in this thesis has already been successfully tested on the RCV there are still aspects that are reasonable to consider and would either improve the search speed or the quality of the overall solution. In the following the most promising improvements are shortly presented.

\section{Variable Resolution Search}
HA* uses a constant cell size and constant arc length for the vertex expansion. Usually it is desirable to increase the resolution as much as computationally possible. This will ensure greater notions of completeness as well as optimality. Completeness will be improved since a coarse resolution underestimates the free space $C_{free}$, making narrow passages appear not traversable without collision. A higher resolution will also create solutions that are closer to the optimum, as opposed to coarse resolutions where the solution oscillates around the optimum. In terms of computational efficiency a variable resolution search can greatly reduce the expansions necessary to converge towards the goal.

The two possibilities to make improvements in the areas of completeness as well as computational efficiency are either locally changing the arc length for the vertex expansion or the resolution of the cells. While locally changing the cell resolution requires a different data structure representing the cells it is easy to increase the arc length used for the vertex expansion. The arc length can be based on the size of the free space it expands to. A convenient representation of this can be achieved using the Voronoi diagram. 

\section{Heuristic Lookup Table}
During the HA* search the constrained heuristic constantly evaluates the shortest distance from the vehicles current configuration to the goal configuration under the assumption that no obstacles exists and the car is constrained by a lower bound turning radius. As this heuristic is not dependent on sensor information it can be completely precomputed and retrieved during run-time.
	
\section{Velocity Profile Generation}
	A reasonable addition to the HA* planner is the calculation of a velocity profile. Based on the smoothed path a reference velocity could be calculated in different ways. A simple approach would be an upper bound lateral acceleration $a_y$ of the vehicle based on the curvature of each segment of the path. If one also wants to consider the yaw rate of the vehicle $\dot{\theta}$ a linear single track model of the vehicle could be used to simulate the lateral dynamics at a given velocity $v_x$. 

\section{Path Commitment and Replanning}
	As the vehicle is progressing towards the goal the sensors will detect new obstacles in the environment that have previously been out of range or covered by other obstacles. In order to incorporate possible changes in the environment in the path planning HA* recomputes the path to the goal with every update of the environment it receives.
	
	This is often not necessary. Given the fact, that the sensor information in the vicinity of the car is of high quality replanning, if at all, does not need to start at the vehicles current position. A path commitment can significantly reduce the planning effort. Commitment to the path means that as new sensor information arrives the path will not be replanned at the vehicle's current position, but rather at the $n$-th vertex that is still in an area where the sensors reliably perceive the environment.
	
	As planning an entire path takes considerably more time than merely checking the same for collisions one has to ask, whether it is feasible to replann a path as opposed to just check the current path for collisions given the updated model of the environment.
	
	Another aspect are dynamic obstacles that temporarily collide with the path. The current version of HA* cannot distinguish between dynamic and static obstacles, as a dynamic obstacle, like a static obstacles, only leaves a binary footprint on the occupancy grid. This will leave the planner to believe that replanning is the right way to solve this problem. While for the static case it would be reasonable to replann based on the new information it is undesirable for dynamic obstacles since the planner does not account for the velocity of the obstacle and hence does not guarantee the path being safe.
	
%\section{Higher Resolution Occupancy Grid}
%As the cell size ($1 m by 1 m$) for the HA* planner and the occupancy grid is the same the free space is underestimated and the size of the car is overestimated.
%\subsection{Jump Point Search}
%\subsection{Reversing 4th Dimension}
%\subsection{Pop Closest to Goal}