\section{Hybrid A* Planner}
As described in \fref{sec:HA} the hybrid A* search expands vertices in continuous rather than discrete space. Using this fact, the action set $U$ for a given vertex $x$ could take any shape. In order to adhere to the constraints imposed by a non-holonomic vehicle, vertex will be expanded by one of three actions; maximum steering left, maximum steering right as well as no steering. This will ensure that the resulting paths are always drivable even though they might result in excessive steering actions.

The velocity of the vehicle is not modeled during the planning phase.
\subsection{Vehicle Constraints}

\subsection{Algorithm}

Under the assumption that the steering actions are either maximum steering right, no steering, or maximum steering left the arc length can be simply expressed as $r\abs{x_\theta- x'_\theta}$, $r$ being the minimum turning radius of the vehicle. 

Calculation of the new states $x'$, with the initial state $x$ consisting of :\\
$x_x, x_y, x_\theta$ the turning radius $r$, the turning angle $\theta$ and distance $d$ as well as the unit vector $e = \left(\begin{smallmatrix}0\\1\end{smallmatrix}\right)$
\begin{description}
  \item[left] \hfill \\
  $r_\theta = x_\theta + \frac{\pi}{2}$\\
  $x'_\theta = x_\theta + \theta$
  \item[right] \hfill \\
  $r_\theta = x_\theta - \frac{\pi}{2}$\\
  $x'_\theta = x_\theta - \theta$
  \item[left and right] \hfill\\
  $r_x = r(e_x\cos(r_\theta) - e_y\sin(r_\theta)) + x_x$\\
  $r_y = r(e_x\sin(r_\theta) - e_y\cos(r_\theta)) + x_y$\\
  $x'_x = (x_x-r_x)\cos\theta - (x_y-r_y)\sin\theta + r_x$\\
  $x'_y = (x_x-r_x)\sin\theta - (x_y-r_y)\cos\theta + r_y$
  \item[straight] \hfill \\
  $x'_x = x_x - d\sin(x_\theta)$\\
  $x'_y = x_y + d\cos(x_\theta)$
\end{description}


\subsection{Heuristics}
underestimating distance, thus nodes expanded at the beginning are getting better in the end, when the real cost is being calculated
\subsubsection{Constrained Heuristic}
A constrained heuristic takes the characteristics of the vehicle into account.
\paragraph{Dubin's Paths}
Shoot for the goal
\subsubsection{Unconstrained Heuristic}
An unconstrained heuristic neglects the characteristics of the vehicle.
\paragraph{Two Dimensional A*}