\chapter{Method}
The second part of this thesis presents the hybrid A* method, its implementation as well as simulation results in detail. This chapter will talk about the method used to solve the navigation problem.

The navigation of a mobile robot in the real as opposed to a discretized world, boils down to a complex, continuous-variable optimization problem. While there are a great variety of optimal and fast planners for discrete space, these planners often produces solutions that are not suitable for non-holonomic vehicles as they are not smooth and do not incorporate the vehicle constraints properly \cite{Dolgov.2008}. Using state lattice approaches these issues have been addressed, however this approach comes with the need of precomputing a huge amount of motion primitives to account for a multitude of different scenarios and issues of connecting the lattice appropriately \cite{Urmson.2008,Ferguson.2008b,Ferguson.2008}.
Other approaches, such as RRT's, that are especially helpful for finding solutions in higher dimensional spaces, do produce continuous solutions but inherently come with disadvantages of being highly nondeterministic and converging towards solutions that are far from the optimum \cite{Karaman.2011}. The sub-optimality of RRT's has been addressed in \cite{Karaman.2011}, where a RRT* version that has proven asymptotic optimality is presented. Due to its basic properties, their application in path planning is only feasiable with numerous extensions to the original RRT (biasing, heuristics, etc.), Kuwata et al. demonstrated this in \cite{Kuwata.2008}.

Building on A*, hybrid A* can be seen as the extension of an optimal, deterministic and complete algorithm. Hybrid A* is resolution complete, deterministic and due to the usage of admissible heuristics as well as path post processing the solutions produced are in the neighborhood of the global optimum. The effective usage of heuristics decreases the expansion considerably and lets the search converge towards the solution quickly.

The hybrid A* planner can be split in three distinct parts. The hybrid A* search that incorporates the vehicles constraints, the heuristics that make the search well informed, allowing for fast convergence; and the path smoothing that improves the found solution using gradient descent.

\input{content/hybrid_a_star}

% PATH SMOOTHING
\input{content/path_smoothing}